PRIMUS: Quiescent Fraction as a Function of Environment and Redshift

### 2014-02-25 qfenv_paper/qf_environment.tex
Updated paper

%define general packages
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{footnote}
\usepackage{courier}

@@

The most dramatic change in galaxy properties during the past eight
billion years has been a remarkable decline in the star-formation rate
of galaxies in the Universe (\citealt{hopkins06a}).  This decline
appears dominated by decreases in the rates of star-formation of
individual galaxies (\citealt{noeske07a}). There is evidence that a
large fraction of the decline associated with strongly
infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).  The
decline does not appear to be due to the quenching of a large
fractions of the star-forming population, as reflected in observations
of the stellar mass function of quiescent and star-forming galaxies
(\citealt{blanton06a, bundy06a, borch06a, moustakas13a}).  These
findings leave little room for the participation of
environmentally-driven quenching in the global census of
star-formation.  As \citet{cooper08a} and others have pointed out,
because the environmental dependence of total star-formation rates at
fixed redshift is relatively small, environmentally effects are
unlikely to cause the overall star-formation rate decline.

Thus, the impact of environment on galaxy formation has to be
interpreted on top of the background of this overall decline affecting
galaxies in all environments.  The most straightforward investigation
of would directly determine the star-forming properties of galaxies as
a function of environment, stellar mass and redshift in a single,
consistently analyzed data set. This analysis can reveal how galaxies
are quenched in the universe over time, quantitatively establish the
contribution of environmental effects to the overall trends, and
reveal whether those trends happen equally in all environments.
However, such an analysis has not been done previously due to the lack
of sufficiently large samples. In this paper, we apply this approach
using the Prism Multi-object Survey (PRIMUS; \citealt{coil11a,
cool13a}), the largest available redshift survey covering the epochs
between $0<z<1$.

@@

In order to obtain the fixed aperture based environment for the galaxies in the target population, 
we first establish a volume limited {\it Environment Defining Population} (EDP) by imposing a fixed 
cumulative number density absolute magnitude cut off. 
By using a fixed cumulative number density for this sample we seek to build an EDP with galaxies that 
have similar populations in all of the redshift bins i.e. accounting for the progenitor bias. 
As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density 
method using a dark matter simulation with abundance matching and a semi-analytic model, respectively, 
cumulative number density method, while it does not precisely account for the scatter in mass accretion or 
galaxy-galaxy mergers, provides a promising tool to compare galaxy populations over a wide range of cosmic time.
In addition we use the highest redshift bin cumulative number density as the fixed number density 
%%%FINISH THIS SENTENCE
Furthermore \cite{Behroozi:2013aa}

\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{fig_smf_cylr2h25_thresh75_bin0_25.png}
        \caption{Stellar mass functions and quiescent fraction for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
    \end{center}
\end{figure*}

@@

For the EDP of the SDSS-{\em GALEX} sample (hereafter simply referred to as the SDSS EDP), 
we do not use the parent sample of the data due to 
the geometry of the combined angular selection function of the SDSS VAGC and {\em GALEX}. 
Instead, since we are not interested in the $FUV, NUV$ values for the EDP, we just use the
SDSS VAGC where the SDSS-{\em GALEX} catalog is derived from. 
Furthermore, we impose a redshift limit $0.0375-0.145$ on the SDSS EDP sample as opposed 
to the redshift range of $0.01-0.2$ in \cite{Moustakas:20133aa}.
This is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright 
galaxies at $z \sim 0.01$. 
In other words, the lower bound for the redshif range was empirically determined by the bright limit of 
the $M_{g}$ versus redshift distribution and the upper bound by the faint limit of the 
$M_{g}$ versus redshift distribution. 
The same fixed cumulative number density method is used on this SDSS EDP. 
Ultimately we use $M_{g,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins 
$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively. 
These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots the absolute magnitude versus the redshift for the EDP galaxies and the target galaxies.

@@

\subsection{Edge Effects} \label{sec:edgeeffect}
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsscale{1.0}
        \plotone{fig_qf_cylr2h25_thresh75_bin0_25.png}
        \caption{Quiescent fraction for galaxies in the $30$ subsamples divided into redshift bins, $0.06-0.145$ (green), $0.2-0.4$ (red), $0.4-0.6$ 
(magenta), $0.6-0.8$ (blue), and $0.8-1.0$ (black) with low, mid, and high environments. The environments were classified using cylindrical aperture of $R=1\rm{Mpc}$ and $H=50\rm{Mpc}$ 
with environment classification thresholds specified in Table \ref{tab:aperture}. The mass bins for the SMFs and QFs have widths $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.3$. 
SMFs for subsamples with the same environment density classification are plotted on panels along the same column: low (left), mid (middle), and high (right) environments. The top
panels plot SMFs for subsamples with star forming galaxies. The middle panels plot the SMFs for subsamples with quiescent galaxies. The bottom panels plot the QFs for the 
corresponding star-forming SMFs and quiescent SMFs in the same environment classification and redshift bin.}
    \end{center}
\end{figure*}

@@

The figures and analysis described in this paper are done using galaxy environment determined from a fixed aperture with $r_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.
The same analysis was repeated for various aperture dimensions: $r_{\rm{ap}} = 0.5, 1, 2, 3 \rm{Mpc}$ and $h_{\rm{ap}} = 25, 50 \rm{Mpc}$. 
Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
The results obtained from using these different are consistent with the results displayed in this paper. 
\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{fig_qffit_cylr2h25_thresh75_bin0_25.png}
        \label{fig:qf}
        \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for low (triangle), mid (square) and high (circle) environments in redshift bins: $0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, and $0.8-1.0$. Comparing these linear fit values in the redshift range for the different environment densities suggest that the change in QFs is indepdent of environment density.}
    \end{center}
\end{figure}

>>>>

%define general packages
\usepackage{epsfig}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{footnote}
\usepackage{courier}

@@

The most dramatic change in galaxy properties during the past eight
billion years has been a remarkable decline in the star-formation rate
of galaxies in the Universe (\citealt{hopkins06a}).  This decline
appears dominated by decreases in the rates of star-formation of
individual galaxies (\cite{Noeske:2007aa}). There is evidence that a
large fraction of the decline associated with strongly
infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).  The
decline does not appear to be due to the quenching of a large
fractions of the star-forming population, as reflected in observations
of the stellar mass function of quiescent and star-forming galaxies
(\cite{Blanton:2006aa},\citealt{bundy06a, borch06a, moustakas13a}).  These
findings leave little room for the participation of
environmentally-driven quenching in the global census of
star-formation.  As \citet{cooper08a} and others have pointed out,
because the environmental dependence of total star-formation rates at
fixed redshift is relatively small, environmentally effects are
unlikely to cause the overall star-formation rate decline.

Thus, the impact of environment on galaxy formation has to be
interpreted on top of the background of this overall decline affecting
galaxies in all environments.  The most straightforward investigation
of would directly determine the star-forming properties of galaxies as
a function of environment, stellar mass and redshift in a single,
consistently analyzed data set. This analysis can reveal how galaxies
are quenched in the universe over time, quantitatively establish the
contribution of environmental effects to the overall trends, and
reveal whether those trends happen equally in all environments.
However, such an analysis has not been done previously due to the lack
of sufficiently large samples. In this paper, we apply this approach
using the Prism Multi-object Survey (PRIMUS; \cite{Coil:2011aa}, 
\cite{Cool:2013aa}), the largest available redshift survey covering the epochs
between $0<z<1$.

@@

In order to obtain the fixed aperture based environment for the galaxies in the target population, 
we first establish a volume limited {\it Environment Defining Population} (EDP) by imposing a fixed 
cumulative number density absolute magnitude cut off. 
By using a fixed cumulative number density for this sample we seek to build an EDP with galaxies that 
have similar populations in all of the redshift bins i.e. accounting for the progenitor bias. 
As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density 
method using a dark matter simulation with abundance matching and a semi-analytic model, respectively, 
cumulative number density method, while it does not precisely account for the scatter in mass accretion or 
galaxy-galaxy mergers, provides a promising tool to compare galaxy populations over a wide range of cosmic time.
In addition we use the highest redshift bin cumulative number density as the fixed number density 
%%%FINISH THIS SENTENCE
Furthermore \cite{Behroozi:2013aa}
\begin{figure*}
  \begin{center}
    \leavevmode
     \label{fig:smf}
     \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_25.eps,height=0.75\textwidth,angle=90}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=2\rm{Mpc}$ and $H=25\rm{Mpc}$ and  
classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.25$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}
    \end{center}
\end{figure*}

@@

For the EDP of the SDSS-{\em GALEX} sample (hereafter simply referred to as the SDSS EDP), 
we do not use the parent sample of the data due to 
the geometry of the combined angular selection function of the SDSS VAGC and {\em GALEX}. 
Instead, since we are not interested in the $FUV, NUV$ values for the EDP, we just use the
SDSS VAGC where the SDSS-{\em GALEX} catalog is derived from. 
Furthermore, we impose a redshift limit $0.0375-0.145$ on the SDSS EDP sample as opposed 
to the redshift range of $0.01-0.2$ in \cite{Moustakas:2013aa}.
This is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright 
galaxies at $z \sim 0.01$. 
In other words, the lower bound for the redshif range was empirically determined by the bright limit of 
the $M_{g}$ versus redshift distribution and the upper bound by the faint limit of the 
$M_{g}$ versus redshift distribution. 
The same fixed cumulative number density method is used on this SDSS EDP. 
Ultimately we use $M_{g,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins 
$0.06-0.145$, $0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively. 
These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots the absolute magnitude versus the redshift for the EDP galaxies and the target galaxies.

@@

\subsection{Edge Effects} \label{sec:edgeeffect}
\begin{figure*}
    \begin{center}
        \leavevmode
        \label{fig:smf}
        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_25.eps,height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction for target galaxies in low (left) and (high) environments
from redshift range $z=0-0.8$. The QFs were calculated using the SMFs specificed in Figure \ref{fig:smf}. We use
lighter shades of orange for the QFs at higher redshifts.}
    \end{center}
\end{figure*}

@@

The figures and analysis described in this paper are done using galaxy environment determined from a fixed aperture with $r_{\rm{ap}} = 1 \rm{Mpc}$ and $h_{\rm{ap}} = 50 \rm{Mpc}$.
The same analysis was repeated for various aperture dimensions: $r_{\rm{ap}} = 0.5, 1, 2, 3 \rm{Mpc}$ and $h_{\rm{ap}} = 25, 50 \rm{Mpc}$. 
Minor adjustments to the environment classification thresholds were adopted in these analyses for the smaller apertures ($r_{\rm{ap}} = 0.5, 1 \rm{Mpc}$ and $r_{\rm{ap}} = 25 \rm{Mpc}$).
The results obtained from using these different are consistent with the results displayed in this paper. 
\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \plotone{fig_qffit_cylr2h25_thresh75_bin0_25.png}
        \label{fig:qf}
        \caption{Quiescent fraction at fiducial mass $\rm{log} (\mathcal{M}/\mathcal{M}_{\odot}) = 10.5$ for 
low (square) and high (circle) environments in the redshift range $z = 0 - 0.8$. The evolution of 
$f_{Q}(\mathcal{M}_{\rm{fid}})$ for galaxies in different environments shows an evolution over the redshift
range that is independent of environment density. Futhermore throughout the redshift range the difference in 
$f_{Q}(\mathcal{M}_{\rm{fid}})$ remains relatively constant and $ < 0.15$.}
    \end{center}
\end{figure}
